Constraint Programming Algorithms used in Gecode

### 2014-06-17 paper.tex
added abbreviations

	\subsubsection{Depth-First Search}
	The idea behind this search algorithm is that every possible combination of variables is examined. In its basic form it can not be applied to problems with infinite domains; for problems with such variable domains it is necessary to use for instance branch-and-bound. Sometimes the depth-first search is also referred to as chronological backtrack search.

	The starting point for the depth-first search is the root node, from where on the algorithm is called recursively. At every node, mainly two steps are executed: First, a constraint propagation to reduce the variable domains and second a branching, which divides the search space into two disjoint subspaces, on which the same algorithm is applied again. The search stops in a leaf of the search tree if either no branching is possible and therefore a valid solution is found, or one or more variable domains are emptied, which indicates that in this leave no possible solution exists.

@@

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming an objective is defined which should be either minimized or maximized, a modified version of the depth-first search can be applied. The only difference is that it evaluates the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search it is possible to add an additional constraint which requires that the new value for the objective must be better than the best achieved so far. Through this enhancement even more subtrees are pruned and the search is faster.

	This algorithm is also complete. Hence, it will always find the best solution, if one exists. This algorithm does not inherit the bad memory characteristics from the depth-first search as only one solution is stored, but the search is still exhaustive and can be very slow, depending on the size of the variable domains.

	\subsubsection{Branch-and-Bound Search}
	A branch-and-bound search is an algorithm for optimization of an objective function under certain constraints and only discrete possible candidates for a solution. The difference to the depth-first search with optimization is the usage of a so-called relaxed optimum, the optimum without consideration of the required discreetness.

@@

	\subsubsection{Limited Discrepancy Search}
	The limited discrepancy search falls into the category of best-first searches and was first mentioned by Harvey and Ginsberg \cite{limitedDiscrepancy}. It depends on branching heuristics for the tree, which are determined through branching strategies. The basic concept is that during a depth-first search a wrong turn close to the root is first of all very expensive. Second, heuristics work worse the farther away from the solution they are applied. Therefore, decisions close to the root node are likely to fail. Consequently, in a depth-first search the worst decisions are the most expensive ones. The limited discrepancy search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretically proven in \cite{limitedDiscrepancy}.

	\subsubsection{Backjumping}
	A specific version of backjumping was already mentioned, the limited discrepancy search, where instead of jumping one node back the algorithm always jumps as far back to the root node as possible. In general this is proven to be better than the chronological backtracking \cite{limitedDiscrepancy}. However, for certain problems it may be possible to find better nodes to jump back. A jump back in the search tree means to detect a so-called nogood decision, which caused the violation of a constraint in the dead end. How these nogoods must be selected and stored to improve the search depends heavily on the specific field and if it is done wrong the backjumping can even be less efficient than a depth-first search \cite[p.~100]{handbookCP}.

>>>>

	\subsubsection{Depth-First Search (DFS)}
	The idea behind this search algorithm is that every possible combination of variables is examined. In its basic form it can not be applied to problems with infinite domains; for problems with such variable domains it is necessary to use for instance branch-and-bound. Sometimes the DFS is also referred to as chronological backtrack search.

	The starting point for the DFS is the root node, from where on the algorithm is called recursively. At every node, mainly two steps are executed: First, a constraint propagation to reduce the variable domains and second a branching, which divides the search space into two disjoint subspaces, on which the same algorithm is applied again. The search stops in a leaf of the search tree if either no branching is possible and therefore a valid solution is found, or one or more variable domains are emptied, which indicates that in this leave no possible solution exists.

@@

	\subsubsection{Depth-First Search with Optimization}
	If in the constraint programming an objective is defined which should be either minimized or maximized, a modified version of the DFS can be applied. The only difference is that it evaluates the objective function for every found solution concerning the constraints and stores during the search only the best one. To accelerate the search it is possible to add an additional constraint which requires that the new value for the objective must be better than the best achieved so far. Through this enhancement even more subtrees are pruned and the search is faster.

	This algorithm is also complete. Hence, it will always find the best solution, if one exists. This algorithm does not inherit the bad memory characteristics from the DFS as only one solution is stored, but the search is still exhaustive and can be very slow, depending on the size of the variable domains.

	\subsubsection{Branch-and-Bound Search}
	A branch-and-bound search is an algorithm for optimization of an objective function under certain constraints and only discrete possible candidates for a solution. The difference to the DFS with optimization is the usage of a so-called relaxed optimum, the optimum without consideration of the required discreetness.

@@

	\subsubsection{Limited Discrepancy Search (LDS)}
	The LDS falls into the category of best-first searches and was first mentioned by Harvey and Ginsberg \cite{limitedDiscrepancy}. It depends on branching heuristics for the tree, which are determined through branching strategies. The basic concept is that during a DFS a wrong turn close to the root is first of all very expensive. Second, heuristics work worse the farther away from the solution they are applied. Therefore, decisions close to the root node are likely to fail. Consequently, in a DFS the worst decisions are the most expensive ones. The LDS solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretically proven in \cite{limitedDiscrepancy}.

	\subsubsection{Backjumping}
	A specific version of backjumping was already mentioned, the limited discrepancy search, where instead of jumping one node back the algorithm always jumps as far back to the root node as possible. In general this is proven to be better than the chronological backtracking \cite{limitedDiscrepancy}. However, for certain problems it may be possible to find better nodes to jump back. A jump back in the search tree means to detect a so-called nogood decision, which caused the violation of a constraint in the dead end. How these nogoods must be selected and stored to improve the search depends heavily on the specific field and if it is done wrong the backjumping can even be less efficient than a DFS \cite[p.~100]{handbookCP}.
